---
title: "Homework 1"
output:
  html_document:
    df_print: paged
---

```{r global_options, include=FALSE}
library(knitr)
library(ggplot2)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)
```

**This homework is due on the deadline posted on edX. Please submit a .pdf file of your output and upload a .zip file containing your .Rmd file. Do NOT include your name or EID in your filenames.**

In this homework you will be working with the `chickwts` dataset built into R. This data set contains weight measurements of chicks fed on different food sources to assess their effectiveness on growth rate.

```{r}
head(chickwts)
```

**Problem 1:** Use ggplot to make a histogram of the `weight` column. Manually choose appropriate values for `binwidth` and `center`. Explain your choice of values in 2-3 sentences.

```{r}
library(ggplot2)

# Create the histogram
ggplot(chickwts, aes(x = weight)) +
  geom_histogram(binwidth = 20, center = 100) +
  labs(title = "Histogram of Chicks' Weight",
       x = "Weight",
       y = "Frequency") +
  theme_minimal()

```

*I chose a binwidth of 20 and a center of 100 based on the distribution of the data. These values provide a clear representation of the weight distribution of the chicks in the Dataset. Adjusting these values may be necessary depending on the specific insights you want to gain from the histogram..*


**Problem 2:** Modify the plot from Problem 1 to show one panel per feed. Hint: Use `facet_wrap()`.

```{r}
library(ggplot2)

# Create the histogram with facet_wrap
ggplot(chickwts, aes(x = weight)) +
  geom_histogram(binwidth = 20, center = 100) +
  labs(title = "Histogram of Chicks' Weight",
       x = "Weight",
       y = "Frequency") +
  facet_wrap(~ feed, ncol = 3) +
  theme_minimal()

```

