---
title: "Project 1"
---

```{r global_options, include=FALSE}
library(knitr)
library(ggplot2)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)
```

**This project is due on the deadline posted on edX. Please submit a .pdf file of your output and upload a .zip file containing your .Rmd file. Do NOT include your name or EID in your filenames.**


**Part 1:** Demonstrate basic command of Markdown by creating a bulleted list with three items, a numbered list with three items, and a sentence that has one word in bold and one word in italics.

- Item 1
- Item 2
- Item 3

1. Numbered Item 1
2. Numbered Item 2
3. Numbered Item 3

This is a **bold** word and this is an *italic* word.


**Part 2:** The `mtcars` dataset contains information on car design and performance in 1974:

```{r}
mtcars
```

Use ggplot to make a line plot of the fuel economy of a car, measured in miles/gallon (column `mpg`), versus its weight (column `wt`).

```{r}

library(ggplot2)


line_plot <- ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_line() +
  labs(x = "Weight", y = "Miles/Gallon", title = "Fuel Economy vs. Weight")
print(line_plot)
```

Now make a scatter plot (using `geom_point()`) of the horse power of a car (`hp`) versus its weight, and color points by its fuel economy.

```{r}

scatter_plot <- ggplot(mtcars, aes(x = wt, y = hp, color = mpg)) +
  geom_point() +
  labs(x = "Weight", y = "Horsepower", title = "Horsepower vs. Weight (Colored by Fuel Economy)")

print(scatter_plot)
```
